---
title: "13-starter-code"
format: docx
editor: visual
---

# Libraries

Import our libraries.

```{r}
# Load packages.
library(tidyverse)
library(tidymodels)
```

# Preprocessing

Before implementing our model, we need to *preprocess the data* to make it appropriate for the model.

```{r}
soup_data <- read_csv("soup_data.csv")
```

Part of the pre-processing in this case is creating our outcome variable. Let's examine the distribution of `Sales`.

```{r}
soup_data |>
  ggplot(aes(x = Sales)) +
  geom_histogram()
```

What do you notice?

If we look at the 80th percentile, it is about \$20,000. In other words, 80% of sales periods have sales that are less than 20,000. We'll use this our cutoff for what defines a `top-selling` period.

```{r}
soup_data |>
  summarize(p95_sales = quantile(Sales, 0.80))
```

Define our top selling variable

```{r}
soup_data <- soup_data |> 
  mutate(top_selling = if_else(Sales > 20000, 1, 0) |> factor())
```

We'll also split the data into training and testing sets.

```{r}
# Split data.
soup_split <- initial_time_split(soup_data, prop = 0.90)
```

# Your Turn!

Define a new recipe called `soup_recipe` based on the training data that prepares data for a model where `top_selling` is our dependent variable and `Any_Price_Decr_Spend` and `Retailer_Trade_Areas` are our independent variables. Include appropriate pre-processing steps and prep the recipe.

```{r}
# Prepare a preprocessing recipe.
(soup_recipe <- training(soup_split) |> 
  recipe(top_selling ~ Any_Price_Decr_Spend + Retailer_Trade_Areas) |> 
  step_log(Any_Price_Decr_Spend, offset = 1) |> 
  step_dummy(Retailer_Trade_Areas) |> 
  prep())
```

Apply the recipe to the training and testing data.

```{r}
# Apply the recipe to the training and testing data.
soup_training <- soup_recipe |>
  bake(training(soup_split))

soup_testing <- soup_recipe |>
  bake(testing(soup_split))
```

# Model Fitting

Specify the model and engine and fit the model. When we *fit* the model (a.k.a., training, calibrating, or estimating the model) we are getting parameter estimates.

```{r}
# Fit a logistic regression.
fit <- logistic_reg() |> 
  set_engine("glm") |> 
  fit(top_selling ~ ., data = soup_training)
```

# Evaluate the Model

Instead of measuring how well a model fits the *data*, we should measure how well a model *predicts*. This predictive fit doesn't have the same risk of overfitting.

Instead of RMSE, we will compute the **accuracy** of the logistic regression. Closer to 1 is better.

```{r}
# Compute model accuracy.
fit |> 
  predict(new_data = soup_testing)|>
  bind_cols(soup_testing) |>
  accuracy(truth = top_selling, estimate = .pred_class)
```

What is the proportion of sales periods that are not top selling?

```{r}
soup_testing |>
  summarize(prop_not_top = mean(top_selling == 0))
```

Accuracy can also be summarized using a **confusion matrix**.

```{r}
# Confusion matrix.
fit |> 
  predict(new_data = soup_testing) |>
  bind_cols(soup_testing) |>
  conf_mat(truth = top_selling, estimate = .pred_class)
```

The `predict` function uses a threshold of `0.5` default. If we want to adjust for a tendency for False Positives or False Negatives, we can use a custom threshold instead.

```{r}
threshold <- 0.45

# Compute model accuracy.
fit |> 
  predict(new_data = soup_testing, type = "prob") |>
  bind_cols(soup_testing) |>
  mutate(pred_y = if_else(.pred_1 >= threshold, 1, 0) |> factor()) |>
  accuracy(truth = top_selling, estimate = pred_y)
```

Confusion matrix based on custom threshold.

```{r}
# Confusion matrix.
fit |> 
  predict(new_data = soup_testing, type = "prob") |>
  bind_cols(soup_testing) |>
  mutate(pred_y = if_else(.pred_1 >= threshold, 1, 0) |> factor()) |>
  conf_mat(truth = top_selling, estimate = pred_y)
```

# Evaluate Parameters

Remember, our goal is to use the model to *estimate* the unobserved parameters from the data. In other words, parameter estimates are the information we are extracting from the data to inform our managerial decision.

```{r}
# Compare parameter estimates.
tidy(fit, conf.int = TRUE) |> 
  ggplot(aes(y = term)) + 
  geom_point(aes(x = estimate)) + 
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high)) +
  geom_vline(xintercept = 0, color = "red")
```

```{r}
# What about interpreting the parameter estimates?
tidy(fit, conf.int = TRUE)
```

# Counterfactuals

Once we have a best-fitting model, we want to predict **counterfactuals**. A counterfactual is a prediction of what will happen if we intervene in the process in a certain way.

```{r}
# Column names, type, and preprocessing needs to match the recipe.
scenarios <- tibble(
  # generate spend on price decreases using 4 values from 0 to 10,000
  # repeat those spend values 4 times, one repetition for each trade area
  Any_Price_Decr_Spend = seq(from = 0, to = 10000, by = 10000 / 3) |> rep(4),
  # generate the trade areas, repeat 4 times for each value of spend on price decreases
  Retailer_Trade_Areas = unique(soup_data$Retailer_Trade_Areas) |> rep(4) |> sort(),
  top_selling = factor(1)
)

scenarios
```

Remember to remove the outcome from `new_data` before using it in `predict()`.

```{r}
# Apply the recipe to the training data.
scenarios <- soup_recipe |>
  bake(scenarios) |> 
  select(-top_selling)

scenarios
```

Since multiple counterfactual scenarios might be predicted to produce a top-selling sales period, we will examine the probability of success for each scenario. In other words, which counterfactual is most likely to result in a top-selling sales period?

```{r}
# Predict success (no prediction intervals).
predict(fit, new_data = scenarios, type = "prob") |> 
  bind_cols(scenarios) |> 
  mutate(Any_Price_Decr_Spend = exp(Any_Price_Decr_Spend)) |> 
  arrange(desc(.pred_1))
```

## Live Coding

Once again, `iFood` has requested our help. They want statistically backed insights into which types of customers have been most likely to respond to their previous marketing campaign(s). Let's perform the appropriate pre-processing and modeling steps to answer their question.

```{r}
(ifood <- read_csv("ifood.csv"))
```

We're going to focus on drivers of response to the most recent campaign.

# Pre-Processing iFood

```{r}
ifood <- ifood |>
  drop_na() |>
  mutate(Kidhome = as.character(Kidhome),
         Response = as.factor(Response))
```

Do the train-test split.

```{r}
# do we need to add strata?
ifood_split <- initial_split(data = ifood, prop = 0.9)
```

```{r}
training(ifood_split)
```

Define pre-processing recipe.

```{r}
# Prepare a preprocessing recipe.
(ifood_recipe <- training(ifood_split) |> 
  recipe(Response ~ Income + Recency + Kidhome) |> 
  step_dummy(Kidhome) |> 
  prep())
```

Pre-process the training and testing data sets.

```{r}
baked_training <- ifood_recipe |>
  bake(training(ifood_split))

baked_testing <- ifood_recipe |>
  bake(testing(ifood_split))
```

Estimate the model for Response.

```{r}
# Fit a logistic regression.
fit <- logistic_reg() |> 
  set_engine("glm") |> 
  fit(Response ~ ., data = baked_training)
```

Evaluate the model on the test data.

```{r}
# Compute model accuracy.
fit |> 
  predict(new_data = baked_testing)|>
  bind_cols(baked_testing) |>
  accuracy(truth = Response, estimate = .pred_class)
```
